Parsing Postfix log files

### 2007-09-19 doc/logparser.tex
Moved all generated files to build subdirectory. Added introduction to graphs section. Added some more stats. Removed generated files from repository, they need to be rebuilt properly.

\input{stats-normal-shuffle-reverse-percentage}

@@

\input{stats-cached-discarded-include-for-discussion}

@@

\includegraphics{logparser-flow-chart.ps}

@@

@@

\subsubsection{Execution time vs file size vs number of lines.}
\label{execution time vs file size vs number lines}
\includegraphics{plot-normal-filesize-numlines.ps}

\subsubsection{Ratio of file size and number of lines to execution time}
\label{execution time vs file size vs number lines factor}
\includegraphics{plot-normal-filesize-numlines-factor.ps}

@@

\subsubsection{Rule hits}
\label{rule hits}
\includegraphics{plot-hits.ps}

\subsubsection{Normal vs shuffled vs reversed ordering}
\label{normal vs shuffled vs reversed ordering}
\includegraphics{plot-normal-shuffle-reverse.ps}

\subsubsection{Percentage increase of shuffled + reversed over normal}
\label{normal vs shuffled vs reversed ordering factor}
\includegraphics{plot-normal-shuffle-factor.ps}
\newline
\includegraphics{plot-normal-reverse-factor.ps}

The worst-case performance of shuffled rules can be seen at log file 30,
where it is equivalent to reversed rules.

@@

\subsubsection{Log 22 distribution by rule}
\label{log22 distribution by rule}
\includegraphics{plot-log22-distribution-by-rule.ps}

@@

\subsubsection{Log 22 line and rule distribution by program}
\label{log22 line and rule distribution by program}
\includegraphics{plot-log22-distribution-versus-rule-count.ps}

@@

\subsubsection{Regex: cached vs discarded}
\label{normal regex vs discard regex}
\includegraphics{plot-cached-discarded.ps}

\subsubsection{Regex: percentage execution time increase}
\label{normal regex vs disarded regex factor}
\includegraphics{plot-cached-discarded-factor.ps}

@@

\input{stats-cached-discarded-include-for-graph}

>>>>

\input{build/stats-normal-shuffle-reverse-percentage}

@@

\input{build/stats-cached-discarded-include-for-discussion}

@@

\includegraphics{build/logparser-flow-chart.ps}

@@

Graphs are an excellent means of displaying data, transforming a
meaningless stream of numbers into an easily comprehensible form, where
anomalies and patterns are immediately obvious.  These graphs are used to
illustrate the topics discussed in section~\ref{rule efficiency}.  The
graphs in the first section cover parser scalability, demonstrating that
its performance scales linearly with input size.  The impact of rule
ordering is shown in section~\ref{rule ordering graphs}, and the lower
impact of rule ordering on larger log files is explained.  The final group
of graphs vividly shows the huge impact that caching compiled regexs has on
parser performance.

@@

\subsubsection{Execution time vs file size vs number of lines.}
\label{execution time vs file size vs number lines}
\includegraphics{build/plot-normal-filesize-numlines.ps}

\subsubsection{Ratio of file size and number of lines to execution time}
\label{execution time vs file size vs number lines factor}
\includegraphics{build/plot-normal-filesize-numlines-factor.ps}

\input{build/stats-normal-filesize-line-count-include}

@@

\label{rule ordering graphs}

\subsubsection{Rule hits}
\label{rule hits}
\includegraphics{build/plot-hits.ps}

\subsubsection{Normal vs shuffled vs reversed ordering}
\label{normal vs shuffled vs reversed ordering}
\includegraphics{build/plot-normal-shuffle-reverse.ps}

\subsubsection{Percentage increase of shuffled + reversed over normal}
\label{normal vs shuffled vs reversed ordering factor}
\includegraphics{build/plot-normal-shuffle-factor.ps}
\newline
\includegraphics{build/plot-normal-reverse-factor.ps}

@@

This non-intuitive effect will not be exhibited by log files in general: in
a normally functioning mail system the impact of rule ordering will scale
linearly with log file size.  The skewed distribution of log lines in the
specific log files creates the anomaly described herein.

\subsubsection{Log 22 distribution by rule}
\label{log22 distribution by rule}
\includegraphics{build/plot-log22-distribution-by-rule.ps}

@@

\subsubsection{Log 22 line and rule distribution by program}
\label{log22 line and rule distribution by program}
\includegraphics{build/plot-log22-distribution-versus-rule-count.ps}

@@

\subsubsection{Regex: cached vs discarded}
\label{normal regex vs discard regex}
\includegraphics{build/plot-cached-discarded.ps}

\subsubsection{Regex: percentage execution time increase}
\label{normal regex vs disarded regex factor}
\includegraphics{build/plot-cached-discarded-factor.ps}

@@

\input{build/stats-cached-discarded-include-for-graph}
